---
title: 'Practice Exam #2'
author: "Buddy Scott"
date: "10/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rstanarm)
library(fivethirtyeight)
library(rsample)
```

```{r q1}
q1 <- US_births_2000_2014 %>%
  group_by(month, year) %>%
  summarize(mean_births = mean(births), .groups = "drop") %>%
  filter(year >= 2003)

q1 %>%
  ggplot(aes(x = month, y = mean_births)) + 
  geom_line() + 
  facet_wrap(~ year) + 
  labs(title = "Number of US Births by Month", x = "Month", 
       y = "Mean # of Births") + 
  theme_minimal() + 
  scale_x_continuous(breaks = c(1, 6, 12), 
                     labels = c("Jan.", "June", "Dec.")) + 
  theme(panel.spacing = unit(0.8, "lines"))

  
```
Highest births always in the late summer / early fall months, while the lowest 
number of births are in the winter (December and January).

```{r q2}
random_sample <- tibble(sample_n(US_births_2000_2014, 500))
nonrandom_sample <- US_births_2000_2014 %>%
  filter(month == 9)

average1 <- US_births_2000_2014 %>%
  summarize(mean_births = mean(births), .groups = "drop")

average2 <- random_sample %>%
  summarize(mean_births = mean(births), .groups = "drop")

average3 <- nonrandom_sample %>%
  summarize(mean_births = mean(births), .groups = "drop")
```
Estimate for overall births and for the random sample are fairly close to each 
other, but estimate for births in September is way higher, corresponding to 
what the graphs showed in question 1 about September being the highest month
in terms of babies being born.

```{r q3}
bootstrap_estimate <- function(x) {
x %>%
  bootstraps(times = 1000) %>%
  mutate(boot = map(splits, ~ analysis(.))) %>%
  mutate(births2 = map(boot, ~pull(., births))) %>%
  mutate(avg_births = map_dbl(births2, ~mean(.)))
}

boot_random <- random_sample %>%
  bootstrap_estimate(.)

boot_nonrandom <- random_sample %>%
  bootstrap_estimate(.)

boot_ci_rand <- boot_random %>%
  pull(avg_births) %>%
  quantile(probs = c(0.025, 0.975))

boot_ci_nonrand <- boot_nonrandom %>%
  pull(avg_births) %>%
  quantile(probs = c(0.025, 0.975))
```
The random confidence interval seems to contain the true value. The CI is 
[11078, 11489] and we found that average to be 11283.04. However, the nonrandom
CI is [11064, 11481] and we found that average to be 11999.09 earlier.

```{r q4}
boot_random <- boot_random %>%
  mutate(sample_type = "Random")

boot_nonrandom <- boot_nonrandom %>%
  mutate(sample_type = "Non-random")

q4 <- bind_rows(boot_random, boot_nonrandom, .id = "sample_type")

q4 %>%
    ggplot(aes(x = avg_births, fill = sample_type)) + 
    geom_density() + 
    geom_vline(xintercept = mean(US_births_2000_2014$births), 
               col = "blue", lty = "dotted") + 
    annotate(geom = "text", 
             x = 11600, 
             y = 0.003, 
             label = "True Answer", 
             col = "blue") +
    theme_classic() + 
    scale_fill_manual(name = "Sample Type",
                      values = c("coral", "pink"),
                      breaks = c("1", "2"),
                      labels = c("Random", "Non-random")) + 
    labs(title = "Bootstrap Distributions from Two Samples",
         subtitle = "Estimating Avg. # of US Births Per Day",
         x = "Avg. births / day", y = "Density")
```

```{r q5}
fit_random <- stan_glm(data = random_sample, births ~ 1, family = gaussian(), 
                      refresh = 0)
rand_ci <- posterior_interval(fit_random, prob = 0.95)

fit_nonrandom <- stan_glm(data = nonrandom_sample, births ~ 1, 
                            family = gaussian(), refresh = 0)
nonrand_ci <- posterior_interval(fit_nonrandom, prob = 0.95)
```

